Particle--in--cell simulations of grazing-incidence x-ray scattering of surfaces upon high--intensity laser irradiation

### 2018-09-29 paper.tex
Small edits.

\title{Theoretical study on grazing-incidence x-ray scattering of  surfaces upon high-intensity laser irradiation}

@@

\author[1]{M. Banjafar}
\author[2]{L. Randolph}
\author[3]{T. Kluge}
\author[3]{M. Bussmann}
\author[1]{A .P. Mancuso}
\author[3]{T. E. Cowan}
\author[1]{C. Fortmann-Grote}
\author[2]{C. Gutt}
\author[1]{M. Nakatsutsumi}

%%\affil[1]{European XFEL GmbH, }

\address[1]{European XFEL GmbH, Holzkopple 4, 22869 Schenefeld, Germany}
\address[2]{Department of Physics, University of Siegen, D-57072 Siegen, Germany}
\address[3]{Helmholtz-Zentrum Dresden-Rossendorf, Bautzner Landstraße 400, 01328 Dresden, Germany}

@@

WDM is a particularly challenging state of matter both from the experimental and from the
theoretical perspective. Being a highly transient state, extremely high temporal
and spatial resolution is required to probe the target's structure and dynamics
using e.g. pulsed x--ray sources. Recently, laser--plasma driven x--ray sources
and free--electron lasers have become the state--of--the--art sources for this
research \cite{Lee2003, Lee2003a}.
X--ray reflectometry (XRR) and grazing incidence x--ray diffraction (GIXD) \cite{TBC} are particularly
sensitive to the sample electron distribution in the plane and in the direction
perpendicular to the target surface.
<+Discuss some difficulties, complex
dynamics+>.

@@

In
Particle--in--cell simulations \cite{} have become the state--of--the--art
numerical technique for hot, strongly ionized plasmas. In the WDM regime, where
collisons and atomic physis become important, the PIC method require substantial
improvements to account for this physics. This is an active area of research.
In this work, we present Particle--in--Cell simulation and x--ray reflectometry
study of interaction of a $10^{16}$ $W/cm^2$ intensity optical laser pulse with
a multilayer target based on an experiment with the same geometry.

>>>>

\title{Particle--in--cell simulations of grazing-incidence x-ray scattering of
surfaces upon high--intensity laser irradiation}

@@

\author[1]{M. Banjafar}
\author[2]{L. Randolph}
\author[3]{T. Kluge}
\author[3]{M. Bussmann}
\author[1]{A .P. Mancuso}
\author[3]{T. E. Cowan}
\author[1]{C. Fortmann-Grote}
\author[2]{C. Gutt}
\author[1]{M. Nakatsutsumi}
%
\address[1]{European XFEL GmbH, Holzkopple 4, 22869 Schenefeld, Germany}
\address[2]{Department of Physics, University of Siegen, D-57072 Siegen, Germany}
\address[3]{Helmholtz-Zentrum Dresden-Rossendorf, Bautzner Landstraße 400, 01328 Dresden, Germany}

@@

WDM is a particularly challenging state of matter both from the experimental and from the
theoretical perspective. Being a highly transient state, extremely high temporal
and spatial resolution is required to probe the target's structure and dynamics
using e.g. pulsed x--ray sources. Recently, laser--plasma driven x--ray sources
and free--electron lasers have become the state--of--the--art sources for this
research \cite{Lee2003, Lee2003a}.
%Optical probes are limited to the first few
%\si{\nm} beneath the surface. X--rays, on the other hand can penetrate deeply
%into the target.
X--ray reflectometry (XRR) and grazing incidence x--ray diffraction (GIXD) \cite{TBC} are particularly
sensitive to the target's surface electron distribution.

@@

In this paper, we apply particle--in--cell simulations to model the
laser--matter interaction of a moderate intensity \si{\fs} laser pulse with
Particle--in--cell simulations \cite{} have become the state--of--the--art
numerical technique for hot, strongly ionized plasmas. In the WDM regime, where
collisons and atomic physis become important, the PIC method require substantial
improvements to account for this physics. This is an active area of research.
In this work, we present Particle--in--Cell simulation and x--ray reflectometry
study of interaction of a $10^{16}$ $W/cm^2$ intensity optical laser pulse with
a multilayer target based on an experiment with the same geometry.
